Species richness destabilizes trophic communities in freshwater ecosystems

### 2020-02-24 manuscript/bef_stability/manuscript.Rmd
compute total effect on BM sem + little updates

# Compute stability, network metrics, etc with ;he new datasets
com_data <- compute_community_temporal_analysis(.op = op_analysis, dest_dir = mypath("data", "species"))

@@

```{r}
# Compute SEMs
stab_sem_rich_beta <- compute_stab_sem_rich_beta(.data = sem_data,
  random_effect = as.formula("~1|basin"))
stab_sem_rich <- compute_stab_sem_rich(.data = sem_data,
  random_effect = as.formula("~1|basin"))
stab_sem_meta <- compute_stab_sem_meta(.data = sem_data,
  random_effect = as.formula("~1|basin"))
stab_sem <- compute_stab_sem(.data = sem_data,
  random_effect = as.formula("~1|basin"))

bm_sem <- compute_prod_sem(.data = sem_data,
  random_effect = as.formula("~1|basin"))
bm_sem_rich <- compute_prod_sem_rich(.data = sem_data,
  random_effect = as.formula("~1|basin"))
bm_sem_rich_beta <- compute_prod_sem_rich_beta(.data = sem_data,
  random_effect = as.formula("~1|basin"))

library(ggraph)
p_stab_sem <- ggpiecewisesem(stab_sem)
p_stab_sem_rich_beta <- ggpiecewisesem(stab_sem_rich_beta)
p_stab_sem_rich <- ggpiecewisesem(stab_sem_rich)

@@

p_bm_sem <- ggpiecewisesem(bm_sem)
p_bm_sem_rich <- ggpiecewisesem(bm_sem_rich)
```

```{r get-sem-coeff}
coef_stab_sem_sum <- coef(stab_sem) %>%
  group_by(Response) %>%
  nest() %>%
  mutate(sum_c = map_dbl(data, ~ sum(.x$Std.Estimate)))

coef_stab_sem <- coef(stab_sem_rich_beta) %>%
  select(- 9) %>%
  filter(P.Value < 0.05)

#cor_mat <- cor(sem_data[, !names(sem_data) %in% c("station", "basin")])
```

@@

## Species richness has a destabilizing effect on community

@@

p_stab_div <- sem_data %>%
  ggplot(aes(x = log_rich_tot, y = log_stab))+
  geom_point() +
  ylim(lim_log_stab) +
  xlim(lim_log_rich_tot) +
  #scale_y_log10() +
  #scale_x_log10() +
  labs(x = richness_lab, y = stab_lab) +
  geom_line(data = stab_div_pred) +
  geom_ribbon(data = stab_div_pred, aes(ymin = conf.low, ymax = conf.high), fill
  = "grey20", alpha = .2) +
  annotate("text", x = 1.0, y = .8, label = make_label_rsq(rsq = stab_div_sum),
    parse = TRUE)

>>>>

# Compute stability, network metrics, etc with ;he new datasets
com_data <- compute_community_temporal_analysis(.op = op_analysis, dest_dir = mypath("data", "classes"))

@@

```{r}
# Compute SEMs
stab_sem_rich <- compute_stab_sem_rich(.data = sem_data,
  random_effect = as.formula("~1|basin"))

bm_sem_rich <- compute_prod_sem_rich(.data = sem_data,
  random_effect = as.formula("~1|basin"))

library(ggraph)
p_stab_sem_rich <- ggpiecewisesem(stab_sem_rich)

@@

p_bm_sem_rich <- ggpiecewisesem(bm_sem_rich)
```

```{r get-sem-coeff}
total_effect_stab_sem <- compute_stab_sem_indirect(sem = stab_sem_rich,
  p_val_thl = 0.05)

total_effect_bm_sem <- compute_bm_sem_indirect(sem = bm_sem_rich,
  p_val_thl = 0.05)

coef_stab_sem <- coef(stab_sem_rich) %>%
  select(- 9) %>%
  filter(P.Value < 0.05)

coef_bm_sem <- coef(stab_bm_rich) %>%
  select(- 9) %>%
  filter(P.Value < 0.05)
```

@@

## Contradictory responses of species richness on total biomass and biomass stability

@@

p_stab_div <- sem_data %>%
  ggplot(aes(x = log_rich_tot, y = log_stab))+
  geom_point() +
  ylim(lim_log_stab) +
  xlim(lim_log_rich_tot) +
  labs(x = richness_lab, y = stab_lab) +
  geom_line(data = stab_div_pred) +
  geom_ribbon(data = stab_div_pred, aes(ymin = conf.low, ymax = conf.high), fill
  = "grey20", alpha = .2) +
  annotate("text", x = 1.0, y = .8, label = make_label_rsq(rsq = stab_div_sum),
    parse = TRUE)
